Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-29 article.tex
Section A.2 rewritten

\textit{Unlike in the
simplified method where each filter $f_1$ and $f_2$ were given equal weight in
the averaging, in the tuned method, we weighted each of the four filters
according to its individual performance on the \textit{normal-1}
dataset.} 
\textcolor{red}{PG: je ne suis pas s\^ur de comprendre comment ces
  poids sont d\'etermin\'es}
$\Rightarrow$

>>>>

Filters $f_1$ and $f_2$ display similar performances and thus were given equal weight in the averaging of the simplified method.
Otherwise, filters $f_3$ and $f_4$ turn out to be, individually, less competitive to provide the signal to compute partial correlation statistics and thus were given smaller weights in the tuned averaging.
In this way, composed functions with $f_3$ or $f_4$ (resp. $f_1$ or $f_2$) contribute less (resp. more) in the tuned averaging.
